Homework

### 2016-06-30 Macro Impacts.tex
small update

0&=k^2\ps{\f{\Sigma_{yz}}{k_yk_z}+\f{\Sigma_{zx}}{k_zk_x}+\f{\Sigma_{xy}}{k_xk_y}}\,.

@@

>>>>

0&=k^2\ps{\f{\Sigma_{yz}}{k_yk_z}+\f{\Sigma_{zx}}{k_zk_x}+\f{\Sigma_{xy}}{k_xk_y}}\,,

@@

i.e.
0&=k_x\Sigma_{yz}+k_y\Sigma_{zx}+k_z\Sigma_{xy}\,.
That is to say $(\Sigma_{yz},\Sigma_{zx},\Sigma_{xy})$ is transverse. Because the only three relevant components are those of this vector, denote $\Sigma=(\Sigma_{yz},\Sigma_{zx},\Sigma_{xy}):=(\Sigma_x,\Sigma_y,\Sigma_z)$.
